Appendix

### 2018-06-11 manuscript/appendix.Rmd
make best partition map in tmap style

```{r source_utils, message=FALSE, results='hide', echo=FALSE, warning=FALSE}

@@

```{r source_functions, echo=FALSE}

@@

```{r iws_vs_nws-gis, cache=TRUE, echo=FALSE, warning=FALSE}
# lagoslakeid <- 6302
# iws <- pull_iws(lagoslakeid, maxsteps = Inf)
# nws <- pull_nws(lagoslakeid, maxsteps = Inf)
# focal_lake <- 
# upstream_lakes <- 
# saveRDS(iws, "../data/iws_extent.rds")
# saveRDS(nws, "../data/nws_extent.rds")

@@

```{r best_partition_maps, cache=TRUE, echo=FALSE}
# setwd("manuscript")

partition_splits <- read.csv("../figures/table_1.csv")
partition_splits <- dplyr::filter(partition_splits, !is.na(splits), 
                                  scale %in% c("nws", "iws"))
partition_splits <- droplevels(partition_splits)
partition_splits$pnames2 <- factor(partition_splits$pnames2, 
                              levels = c("cd", "ll", "la", "sd", "bf", "sr"))
partition_splits <- dplyr::filter(partition_splits, d_k > 0.2)

@@

# pull the lower partition group as an sf object
get_sub <- function(dt, col_name, split_value){
  coordinatize(
    dplyr::filter(dt, UQ(rlang::sym(as.character(col_name))) <= split_value), 
    "lat", "long")
}

lower_nws_maps <- lapply(which(partition_splits$scale == "nws"), 
                         function(x) {
                           nes_sub <- get_sub(nes_nws, 
                                              partition_splits[x, "nws_names"],
                                              partition_splits[x, "splits"])

                           nes_sf_temp <- nes_sf
                           st_geometry(nes_sf_temp) <- NULL
                           na_rows <- !is.na(
                    nes_sf_temp[,as.character(partition_splits[x, "nws_names"])])

                           ggplot() + 
                             geom_sf(data = us_states) +
                             geom_sf(data = nes_sf, 
                                     color = viridis::viridis(1, begin = 0),
                                     size = 1.4) + 
                             geom_sf(data = nes_sub,
                                     color = viridis::viridis(1, begin = 0.5), 
                                     size = 1) + 
                             coord_sf(datum = NA) + 
                             ggtitle(break_word(partition_splits[x, "abb"], 12)) + 
                             theme(plot.margin = unit(c(0, -0.1, 0, -0.1), "cm"), 
                               plot.title = element_text(face = "plain", size  = 12))
                         })

lower_nws_maps <- lower_nws_maps[
  match(levels(partition_splits$pnames2), 
        partition_splits$pnames2[which(partition_splits$scale == "nws")])
  ]

plot_grid(plotlist = lower_nws_maps[2],
         ncol = 1, nrow = 1, align = "v")

>>>>

```{r source_utils, message=FALSE, results='hide', echo=FALSE, warning=FALSE}
# setwd("scripts")
# source("99_utils.R")
```

@@

```{r source_functions, echo=FALSE, warning=FALSE, message=FALSE}

@@

```{r iws_vs_nws-gis, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
# lagoslakeid <- 6302
# iws <- pull_iws(lagoslakeid, maxsteps = Inf)
# nws <- pull_nws(lagoslakeid, maxsteps = Inf)
# focal_lake <- 
# upstream_lakes <- 
# saveRDS(iws, "../data/iws_extent.rds")
# saveRDS(nws, "../data/nws_extent.rds")

@@

```{r best_partition_maps, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(tmap)
library(sf)
library(LAGOSNE)
library(USAboundaries)
library(dplyr)

results_table <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
ll_split <- dplyr::filter(results_table, 
                          nws_names == "avg_link_length" & 
                          scale == "nws")$splits

nes_nws <- mutate(nes_nws, grp = ifelse(avg_link_length > ll_split, 
                                  "High", "Low"))

@@

us <- USAboundaries::us_boundaries()
us <- us[unlist(lapply(st_intersects(us, nes_sf), function(x) length(x) > 0)),]
us <- filter(us, stusps != "AR")

nes_extent <- group_by(us, jurisdiction_type)
nes_extent <- st_union(nes_extent)
nes_extent <- as_Spatial(nes_extent)

palette <- c(viridis::viridis(1, begin = 0),
             viridis::viridis(1, begin = 0.5))

# palette <- c("black",
#               "black")

(m_nes <- tm_shape(us) + tm_polygons() +
          tm_shape(nes_extent) + tm_borders(lwd = 2) +
          tm_shape(dplyr::filter(nes_sf, !is.na(grp))) + tm_dots("grp", palette = palette,
                                 size = 0.15, legend.show = TRUE, 
                                 title = "Average Link Length")) +
          # tm_credits("National Eutrophication Survey") +
          tm_layout(frame = FALSE,
                    legend.outside = FALSE,
                    legend.stack = "horizontal")
```

```{r plot_tree_example, echo=FALSE, fig.width=2, fig.height=3}
plot_tree(gettree(readRDS("../data/nws/linklength_forest.rds")), 
          title = "Link Length")
```

```{r partition_example_scatter, fig.height=2, fig.width=2.2}
results_table <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
ll_split <- dplyr::filter(results_table, 
                          nws_names == "avg_link_length" & 
                          scale == "nws")$splits

nes_nws <- mutate(nes_nws, grp = ifelse(avg_link_length > ll_split, 
                                  "Higher", "Lower"))

ggplot(data = dplyr::filter(nes_nws, 
                     !is.na(avg_link_length))) + 
         geom_point(aes(x = avg_link_length, 
                                        y = p_percent_retention, 
                                        color = grp), 
                                    size = 2) + 
  scale_color_manual(values = c(viridis::viridis(1, begin = 0), 
                     viridis::viridis(1, begin = 0.5))) +
  ylab("P Retention") + xlab("Avg. Link Length") + 
  geom_vline(xintercept = ll_split) + 
  theme(legend.position = "none") 
```
